Procurements of the Canadian Government, Ballooning Military Awards for Fighter Jets

### 2024-12-04 paper/paper.qmd
adde abstract and refrences

---
title: "Procurements of the Canadian Government, Runaway Military Contracts"
author: 
  - Robert Ford
thanks: "Code and data are available at: https://github.com/Ford-Robert . Special thanks to Professor Rohan Alexander for motivating this project, providing key support and insight, and demostrating the crucial skills required in modern statistical analysis. Check out his excellent book: https://tellingstorieswithdata.com/"
date: today
date-format: long
abstract: "TODO First sentence. TODO Second sentence. TODO Third sentence. TODO Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Data was analyzed through the R programming software [@citeR], and `RSelenium` [@rselenium] with `rvest` [@rvest] were used to support a web scraping script to download all data. Additional packages such as `tidyverse` [@tidyverse], `knitr` [@knitr], `actuar` [@actuar], `readr` [@readr], `stringr` [@stringr], `broom` [@broom] and `dplyr` [@dplyr] were used to help clean, simulate, analyze, and test the data. The presentation of this data using tables and graphs was made possible by r-packages; `ggplot2` [@ggplot2], `lubridate` [@lubridate], `kableExtra` [@kable], and `zoo` [@zoo]. All colours are taken from `RColorBrewer` [@colorbrewer]

@@

>>>>

---
title: "Procurements of the Canadian Government, Ballooning Military Awards for Fighter Jets"
author: 
  - Robert Ford
thanks: "Code and data are available at: https://github.com/Ford-Robert . Special thanks to Professor Rohan Alexander for motivating this project, providing key support and insight, and demostrating the crucial skills required in modern statistical analysis. Check out his excellent book: https://tellingstorieswithdata.com/"
date: today
date-format: long
abstract: "This paper gathers data on Canadain Federal Procurement Awards, uses a series of visualizations to analyse the data, builds two linear models to compare general government procurements and military procurements. Over the last three years the Canadian military has tripled their spending in an effort to aquire next generation fighter jets and train pilots, while every other government agency has atrophied. This spending concerns every Canadian citizen and often goes undercovered compared to analysis of the governments general budget."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Data was analyzed through the R programming software [@citeR], and `RSelenium` [@rselenium] with `rvest` [@rvest] were used to support a web scraping script to download all data. Additional packages such as `tidyverse` [@tidyverse], `knitr` [@knitr], `actuar` [@actuar], `arrow` [@arrow], `readr` [@readr], `stringr` [@stringr], `broom` [@broom] and `dplyr` [@dplyr] were used to help clean, simulate, analyze, and test the data. The presentation of this data using tables and graphs was made possible by r-packages; `ggplot2` [@ggplot2], `lubridate` [@lubridate], `kableExtra` [@kable], and `zoo` [@zoo]. All colours are taken from `RColorBrewer` [@colorbrewer]

@@

# Contract Surveys {#sec-surveys}
